---
title: "Project 2: projectpackage Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{projectpackage Tutorial}

  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
projectpackage is an R package for cross validation classification, t- test and testing hypotheses.

```{r setup}

#instructions for how to install your package from Github
library(projectpackage)
```


```{r}


```



```{r}
#A tutorial for my_t.test
#hypothesis: mean of the lifeExp data from my_gapminder equals to 60
#alternative hypothesis: mean of the lifeExp data from my_gapminder does not equal to 60
my_t_test(x=(my_gapminder$lifeExp),alternative="two sided",mu = 60)


#hypothesis: mean of the lifeExp data from my_gapminder equals to 60
#alternative hypothesis: mean of the lifeExp data from my_gapminder is smaller than 60
my_t_test(x=(my_gapminder$lifeExp),alternative="less",mu = 60)

#hypothesis: mean of the lifeExp data from my_gapminder equals to 60
#alternative hypothesis: mean of the lifeExp data from my_gapminder is larger than 60
my_t_test(x=(my_gapminder$lifeExp),alternative="greater",mu = 60)

```
For the first t-test, we observe P = 0.09322877. Therefore we conclude that we have sufficient evidence to reject the null hypothesis and conclude that the true mean life expectancy is not equal to 60.

For the second t-test, we observe P = 0.9533856 Therefore we conclude that we do not have sufficient evidence to reject the null hypothesis. Therefore, we cannot conclude that the true mean life expectancy is smaller than 60.

For the third t-test, we observe P = 0.04661438. Therefore we conclude that we  have sufficient evidence to reject the null hypothesis and conclude that the true mean life expectancy is greater than 60.
```{r}
#A tutorial for my_lm
#Demonstrate a regression using lifeExp as your response variable and gdpPercap and continent as explanatory variables
lm_result <- my_lm(lifeExp ~gdpPercap+continent, data = my_gapminder)

#Write the hypothesis test associated with the gdpPercap coefficient.
my_t_test(x= my_gapminder$gdpPercap, alternative="less", mu = 4.452704e-04)

#plot the Actual vs. Fitted values.
library(ggplot2)
x <- my_gapminder$gdpPercap
y <- my_gapminder$lifeExp
fitting_plot <- ggplot(lm_result, aes(x=x, y=y)) +
        geom_point(aes(x = df_train$x, y = df_train$y, col="Actual")) +
        geom_point(aes(x = df_test$x, y = df_test$y, col="Fitted value")) +
        labs(subtitle = paste("Testing Error:", round(test_err_k, 3))) + 
        geom_line(aes(y = fitted(lm_fit_k[[10]])), col = "red", lwd = 1.5) +
        theme_bw()
testing_error_plot
```
The Estimate contains two rows: the intercept and the slope. The intercept represents the expected value of life Expectancy given the average of gdpPercap and continent of all data. In average, it takes an average datapoint in my_gapminder 1 unit of change in gdpPercap result in a change of 47.88 in life Expectancy.

The slope of 4.45*10^-4 means that for every increase in gdpPercap, the Estimate increase by 4.452704e-04.

The coefficient Standard Error measures the average amount that the coefficient estimates vary from the actual average value of our response variable. Here, it is saying that the life Expectancy can vary by 2.349795e^-5 year. 

The coefficient t-value is a measure of how many standard deviations our coefficient estimate is far away from 0. here, t-value of 18.94 means that there is a relationship between the response variable life Expectancy, and the explanatory variables gdpPercap and continent.

The Pr(>t) acronym found in the model output relates to the probability of observing any value equal or larger than t. A small p-value indicates that it is unlikely we will observe a relationship between the explanatory variables gdpPercap and continen, and response variables life Expectancy due to chance. here, p-value equals to 8.55e^-73, which means that there are 8.55e^-71 percent chance of observing this relationship by chance.


```{r}
#A tutorial for my_knn_cv using my_penguins.


```

```{r}
#A tutorial for my_rf_cv


```

